---
title: "The World's Billionaires"
output: 
  flexdashboard::flex_dashboard:
       orientation: columns 
       social: menu
       source_code: embed
       #css: style.css
runtime: shiny
---

```{r warning=FALSE, message=FALSE, include=FALSE}
# R Packages

library(readr)
library(DT)
library(tidyverse)
library(dplyr)
library(gganimate)
library(plotly)
library(shiny)
#library(shinythemes)
library(flexdashboard)
library(rsconnect)
library(leaflet)
library(crosstalk)

continents <- read.csv('continents.csv')
continents <- continents %>% select(c(Country,Continent))
db11 <- read.csv('Billionaire 2011 - Sheet1.csv', header = TRUE)
db12 <- read.csv('Billionaire 2012 - Sheet1.csv', header = TRUE)
db13 <- read.csv('Billionaire 2013 - Sheet1.csv', header = TRUE)
db14 <- read.csv('Billionaire 2014 - Sheet1.csv', header = TRUE)
db15 <- read.csv('Billionaire 2015 - Sheet1.csv', header = TRUE)
db16 <- read.csv('Billionaire 2016 - Sheet1.csv', header = TRUE)
db17 <- read.csv('Billionaire 2017 - Sheet1.csv', header = TRUE)
db18 <- read.csv('Billionaire 2018 - Sheet1.csv', header = TRUE)
db19 <- read.csv('Billionaire 2019 - Sheet1.csv', header = TRUE)
db20 <- read.csv('FB_2020.csv', header = TRUE)
db21 <- read.csv('FB_2021.csv', header = TRUE)
db22 <- read.csv('FB_2022.csv', header = TRUE)

# All of the data did not have the column for Continents. Hence, I merged the data with the data of the continents.
db11 <- left_join(db11,continents, by = 'Country')
db12 <- left_join(db12,continents, by = 'Country')
db13 <- left_join(db13,continents, by = 'Country')
db14 <- left_join(db14,continents, by = 'Country')
db15 <- left_join(db15,continents, by = 'Country')
db16 <- left_join(db16,continents, by = 'Country')
db17 <- left_join(db17,continents, by = 'Country')
db17$NetWorth <- (as.numeric(db17$NetWorth)) # Net Worth had a character type
db18 <- left_join(db18,continents, by = 'Country')
db19 <- left_join(db19,continents, by = 'Country')
db19$NetWorth <- (as.numeric(db19$NetWorth))
db20 <- left_join(db20,continents, by = 'Country')
db20$NetWorth <- (as.numeric(db20$NetWorth))
db21 <- left_join(db21,continents, by = 'Country')
db21$Age <- as.numeric(db21$Age)
db22 <- left_join(db22, continents, by = "Country")

library(DT)
db11_DT <- datatable(db11)
db12_DT <- datatable(db12)
db13_DT <- datatable(db13)
db14_DT <- datatable(db14)
db15_DT <- datatable(db15)
db16_DT <- datatable(db16)
db17_DT <- datatable(db17)
db18_DT <- datatable(db18)
db19_DT <- datatable(db19)
db20_DT <- datatable(db20)
db21_DT <- datatable(db21)
db22_DT <- datatable(db22)
```



Distribution of Net Worth over the Continents
===
Inputs {.sidebar}
------------------------------------------------------------

### Analysis on Forbes Billionaire List 2022
The data used for the visualization represents the World's Billionaire list published by Forbes magazine . This data was downloaded from Kaggle.com. 
```{r}
# Choose a color for border
selectInput(inputId = 'Color_border',
            label = 'Choose a Color for border',
            choices =  colors())

# Choose a color for fill
selectInput(inputId = 'Color_fill',
            label = 'Choose a Color for fill',
            choices =  colors())
```

Column {data-width=150, .tabset}
--------------------------------------------------------------------

### Bar plot for the Networth distribution over the conitnents - 2022

```{r}

dbp22 <- db22 %>%
  drop_na()%>%
  group_by(Continent) %>%
  summarise(Sum = sum(NetWorth), count = n())

#create a histogram from inputs
renderPlotly(ggplot(dbp22,aes(x= Continent,y = Sum))+
             geom_bar(fill=input$Color_fill,
                            col=input$Color_border,
                      stat = "identity")+
             labs(y = 'Sum in Billion Dollars'))

```

### Bar plot for the Networth distribution over the conitnents - 2021

```{r}

dbp21 <- db21 %>%
  drop_na()%>%
  group_by(Continent) %>%
  summarise(Sum = sum(NetWorth), count = n())

#create a histogram from inputs
renderPlotly(ggplot(dbp21,aes(x= Continent,y = Sum))+
             geom_bar(fill=input$Color_fill,
                            col=input$Color_border,
                      stat = "identity")+
             labs(y = 'Sum in Billion Dollars'))

```

### Bar plot for the Networth distribution over the conitnents - 2020

```{r}
dbp20 <- db20 %>%
  drop_na()%>%
  group_by(Continent) %>%
  summarise(Sum = sum(NetWorth), count = n())

#create a histogram from inputs
renderPlotly(ggplot(dbp20,aes(x= Continent,y = Sum))+
             geom_bar(fill=input$Color_fill,
                            col=input$Color_border,
                      stat = "identity")+
             labs(y = 'Sum in Billion Dollars'))

```


Interactive Data Table for 2022
===
Inputs {.sidebar}
-----------------------------------------------------------------

```{r}
st1 <- db22
st <- SharedData$new(st1)
```

### Filters
```{r filter_section}

filter_select(
  id = "Country",
  label = "Country",
  sharedData = st,
  group = ~Continent
)

bscols(
  filter_checkbox(
    id = 'Continent',
    label = 'Continent',
    sharedData = st,
    group = ~Continent
  )
)

```


Column {data-width = 800}
------------------------------------------------------

### Datatable


```{r filter_table}
datatable(st)
```

Data
===

## Review Data Of Dataset {data-width=100, .tabset}

The tables below shows the data that was used for the analysis. Sources: Forbes Billionaire List

### Billionaire's list- 2011

```{r ,echo = FALSE}
db11_DT   
```

### Billionaire's list- 2012

```{r ,echo = FALSE}
db12_DT
```

### Billionaire's list- 2013

```{r ,echo = FALSE}
db13_DT
```

### Billionaire's list- 2014

```{r ,echo = FALSE}
db14_DT
```

### Billionaire's list- 2015

```{r ,echo = FALSE}
db15_DT
```

### Billionaire's list- 2016

```{r ,echo = FALSE}
db16_DT
```

### Billionaire's list- 2017

```{r ,echo = FALSE}
db17_DT
```

### Billionaire's list- 2018

```{r ,echo = FALSE}
db18_DT
```

### Billionaire's list- 2019

```{r ,echo = FALSE}
db19_DT
```

### Billionaire's list- 2020

```{r ,echo = FALSE}
db20_DT
```

### Billionaire's list- 2021

```{r ,echo = FALSE}
db21_DT
```

### Billionaire's list- 2022

```{r ,echo = FALSE}
db22_DT
```